Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY

### 2015-11-16 Manuscript/Manuscript.Rnw
incorporating Joe's edits

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Intelligence and Age at First Intercourse: Cause or Confound?}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.txt}}
%
% Abstract
\abstract{Last compile was \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional data; Intelligence; Quasi-Experimental}
%
\begin{document}
\maketitle
%
%%%%%%%%%%%% R %%%%%%%%%%%%
<<sweave,echo=FALSE>>=
  options(width=60)
  options(scipen=999)
  options(digits=3)
  options(width=60)

  listing <- function(x, options){
    paste("\\begin{lstlisting}[style=Rsettings]\n",
      x, "\\end{lstlisting}\n", sep = "")}
  knit_hooks$set(source=listing, output=listing)
    knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage{xcolor}', x, fixed = TRUE)})
@
<<setup, include=FALSE,cache=FALSE>>=
# Libraries
## Install Most Current Version
library(devtools)#;dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("harrelfe/Hmisc");dev_mode(on=F)
## Attach Remaining
library(corrplot)
library(ggplot2);library(ggExtra)
library(Hmisc)
library(MplusAutomation)
library(NlsyLinks)
library(plyr);library(psych)
library(stargazer)
library(tables)
library(xtable)
#
# File Structure
file_drive= "C:"
##file_drive="E:"
directory = paste0(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI")
#
# Functions
## source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")
## cor_1star
### Prints out clean correlation matrix. If you want to replace the upper triangle with the sample size, toggle include.n, whose default is FALSE.
cor_1star <- function(x,digit=3,sig=.05,include.n=FALSE){ 
  require(Hmisc) 
  x <- as.matrix(x) 
  R <- rcorr(x)$r 
  p <- rcorr(x)$P

>>>>

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.txt}}
%
% Abstract
\abstract{Last compile was \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\begin{document}
\maketitle
%
%%%%%%%%%%%% R %%%%%%%%%%%%
<<sweave,echo=FALSE>>=
  options(width=60)
  options(scipen=999)
  options(digits=3)
  options(width=60)

  listing <- function(x, options){
    paste("\\begin{lstlisting}[style=Rsettings]\n",
      x, "\\end{lstlisting}\n", sep = "")}
  knit_hooks$set(source=listing, output=listing)
@
<<setup, include=FALSE,cache=FALSE>>=
# Libraries
## Install Most Current Version
library(devtools)#;dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("harrelfe/Hmisc");dev_mode(on=F)
## Attach Remaining
library(corrplot)
library(ggplot2);library(ggExtra)
library(Hmisc)
library(MplusAutomation)
library(NlsyLinks)
library(plyr);library(psych)
library(stargazer)
library(tables)
library(xtable)
#
# File Structure
file_drive= "C:"
##file_drive="E:"
directory = paste0(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI")
#
# Functions
## source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")
## cor_1star
### Prints out clean correlation matrix. If you want to replace the upper triangle with the sample size, toggle include.n, whose default is FALSE.
cor_1star <- function(x,digit=3,sig=.05,include.n=FALSE){ 
  require(Hmisc) 
  x <- as.matrix(x) 
  R <- rcorr(x)$r 
  p <- rcorr(x)$P

### 2015-11-16 Manuscript/Manuscript.tex
incorporating Joe's edits

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Intelligence and Age at First Intercourse: Cause or Confound?}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.txt}}
%
% Abstract
\abstract{Last compile was \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional data; Intelligence; Quasi-Experimental}
%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle
%
%%%%%%%%%%%% R %%%%%%%%%%%%

>>>>

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.txt}}
%
% Abstract
\abstract{Last compile was \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle
%
%%%%%%%%%%%% R %%%%%%%%%%%%
